%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Edyta Zugaj} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{Wroclaw, Poland} 
\moveleft.5\hoffset\centerline{(+48)789357799}
\moveleft.5\hoffset\centerline{edith.zugaj@gmail.com}


%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  

Seeking a position to enhance my skills and abilities in the IT, the most desired technologies are C/C++, embedded applications, telecom, audio/video processing. I would be happy to try other languages like Swift, ObjC, Java, JavaScript. I have positive attitude to work in international environment.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl M.Sc.,} Control Engineering and Robotics, minor: robotics \\
Wroclaw University of Technology, Faculty of Electronics \hfill 2005 - 2010\\
\\
{\sl B.Sc.,} Mathematics, specialization: theoretical mathematics\\
Wroclaw University, Mathematics and Computer Science Department, \hfill 2008 - 2010\\
\\
{\sl B.Sc.,} Computer Science and Econometrics\\
University of Computer Science and Economics in Olsztyn, \hfill 2002 - 2005\\

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl Senior Software Engineer} \hfill March 2016 - now\\
Dolby Poland Sp. z o.o., Wroclaw, Poland

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Development and maintenance of iOS SDK for \href{https://docs.dolby.io/communications-apis/docs/overview-introduction}{dolby.io} communication API. 
\item Porting audio conference client library to WebAssembly, which was then integrated to Web SDK for dolby.io communication API.
\item Development of cross-platform audio conference client library.
\item Maintenance of cross-platform cross-architecture intrinsic library.
\item Porting audio processing libraries written in C/C++ to following platforms: Qualcomm QDSP6, ARM7/8, Xtensa LXn DSP and for operating systems: Android and iOS.
\end{itemize}

{\sl Software Engineer} \hfill April 2011 - March 2016  \\
Nokia Sp. z o.o., Wroclaw, Poland
\begin{itemize} 
\item Development and maintenance of eNB LTE PHY (uplink) on TI C6000 processors family. This layer is responsible for decoding user data that a base station receives from a mobile phone. Porting Matlab model to C/C++.
\item Porting eNB LTE PHY (uplink) to the new TI DSP processor.
\end{itemize} 
Espotel Poland Sp. z o.o., Wroclaw, Poland
\begin{itemize}
\item Development and maintenance of C/ASM drivers for peripherals of TI C6000 processors for eNB base-band modules.
\end{itemize} 


{\sl Junior Software Engineer} \hfill August 2010 - March 2011\\
Red Sky Sp. z o.o., Wroclaw, Poland

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Development of C++ library for distributed file system.

\end{itemize}
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{SKILLS} 

Currently working with Swift, ObjC, C++; hands on experience with: WebAssembly, JavaScript, ASM for QDSP, ASM for ARMv7/8, ASM for Tensilica LX, ASM for TI C6000, Matlab.

\end{resume}
\end{document}